### 2014-11-03 simulation.Rmd
.

# Trace plot of the MCMC run:
```{r, results="asis", echo=FALSE, fig.width=12, fig.height=7, fig.align='center'}
if (class(model)=="contextMCMC") {
    subseq <- seq(1,nrow(model@results$batch),length.out=min(1000,nrow(model@results$batch)))
    x <- model@results$batch[subseq,]
    colnames(x) <- rownames(mr_compare)[model@results$use.par]
    matplot( model@results$blen*subseq, x, type='l', col=1:5, lty=1:6, xlab='number of MCMC iterations' )
    abline(h=mr_compare$simulated[model@results$use.par], col=1:5, lty=1:6)
    legend("topright",legend=colnames(x),col=1:5,lty=1:6)
} else {
    cat("Not an MCMC run.")
}
```

>>>>

# Trace plot of the MCMC run:
```{r, results="asis", echo=FALSE, fig.width=12, fig.height=7, fig.align='center'}
if (class(model)=="contextMCMC") {
    subseq <- seq(1,nrow(model@results$batch),length.out=min(1000,nrow(model@results$batch)))
    x <- model@results$batch[subseq,]
    colnames(x) <- rownames(mr_compare)[model@results$use.par]
    param_sizes <- floor(log10(abs(mr_compare$simulated)+1e-4)/2)
    param_sizes <- param_sizes[model@results$use.par]
    for (k in unique(param_sizes)) {
        print( 
            matplot( model@results$blen*subseq, x[,param_sizes==k], type='l', col=1:5, lty=1:6, xlab='number of MCMC iterations' )
            abline(h=mr_compare$simulated[model@results$use.par], col=1:5, lty=1:6)
            legend("topright",legend=colnames(x)[param_sizes==k],col=1:5,lty=1:6)
          )
    }
} else {
    cat("Not an MCMC run.")
}
```
